### 2022-01-06 experiments.tex
writing

@@

We begin with a simple analysis of the stability of the Plant, as \ac{CLEAVE} allows for straightforward and repeatable analysis of relevant metrics.  
For instance, \cref{fig:topple:fraction} shows a visualization of the fraction of plants that toppled in each scenario.
These Plants were identified simply by analyzing the emulation data --- instances whose pendulum angles reached values above a certain value\footnote{This value will depend on the parametrization of the controller, and in this case corresponds to \SI{20}{\degree}, or \SI{0.35}{\radian}} were marked as ``toppled''.

@@

\Ac{CLEAVE} also allows for more fine-grained analysis of stability.
\Cref{fig:topple:rms} shows the \ac{RMS} of the angles for each setup, averaged over all repetitions of each experiment.

\begin{figure}
    \centering
    \includegraphics[width=.8\columnwidth]{angle_rms.png}
    \caption{RMS}%
    \label{fig:topple:rms}
\end{figure}

When it comes to network reliability, mean packet losses for all setups were below \SI{0.15}{\percent}. 
\todo[inline]{Discuss which network results to add.}

>>>>

\todo[inline]{Capacity experiment description.}

@@

\subsubsection{Single Plant Scenario}

We begin with a simple analysis of the stability of the Plant, as \ac{CLEAVE} allows for straightforward and repeatable analysis of relevant metrics.  
For instance, \cref{fig:topple:fraction} shows a visualization of the fraction of plants that toppled in each scenario.
These Plants were identified simply by analyzing the emulation data --- instances whose pendulum angles reached values above a certain value\footnote{This value will depend on the parametrization of the controller, and in this case corresponds to \SI{20}{\degree}, or \SI{0.35}{\radian}.} were marked as ``toppled''.

@@

\Ac{CLEAVE} also allows for more fine-grained analysis of stability.
\Cref{fig:topple:rms} shows the \ac{RMS} of the angles for each setup, averaged over all repetitions of each experiment.
This figure shows an intuitive but important result --- less stable setups show higher amplitude in the oscillations of their penduli.

\begin{figure}
    \centering
    \includegraphics[width=.8\columnwidth]{angle_rms.png}
    \caption{\Ac{RMS} of the pendulum angles averaged over all runs for each scenario.
    Error bars indicate \SI{95}{\percent} \acp{CI}.}%
    \label{fig:topple:rms}
\end{figure}

Finally, we showcase \ac{CLEAVE}'s ability to obtain network performance data from the experiments.
\Cref{fig:network} shows average \acp{RTT}s and packet losses per scenario.

\begin{figure}
    \centering
    % \includegraphics[width=.8\columnwidth]{angle_rms.png}
    \caption[caption]{Mean \acp{RTT} and packet losses for each scenario; \acp{RTT} were calculated by subtracting the synthetic delay from the absolute end-to-end latency\textsuperscript{a}. Error bars indicate \SI{95}{\percent} \acp{CI}.}%
    \small\textsuperscript{a} The systematic offset of \SI{2}{\milli\second} on scenarios with synthetic delay is an artifact of our implementation, and will be fixed in the next release of the framework.
    \label{fig:network}
\end{figure}

\todo[inline]{Discuss which network results to add.}
